Formalizing Stack Safety as a Security Property

### 2022-12-07 submission5/core.tex
fix typo

A {\em machine state} \(\mach\) is a map from elements to a set \(\mathcal{V}\) of
\emph{values}. Each value \(v\) contains a \emph{payload} word, written \(|v|\) (\(|\cdot|\).
The details of value structure depend on the specific machine being modelled;  
intuitively, the payload represents the part of the value that is relevant to
the behavior of the basic machine, while the rest of the value may contain
information relevant to a hardware enforcement mechanism (such as a tag).
We write \(\mach[\component]\) to denote the value at
\(\component\) of \(\mach\) and \(\mach[v]\) to denote the value at \(|v|\) if
defined.

>>>>

A {\em machine state} \(\mach\) is a map from elements to a set \(\mathcal{V}\) of
\emph{values}. Each value \(v\) contains a \emph{payload} word, written \(|v|\).
The details of value structure depend on the specific machine being modelled;  
intuitively, the payload represents the part of the value that is relevant to
the behavior of the basic machine, while the rest of the value may contain
information relevant to a hardware enforcement mechanism (such as a tag).
We write \(\mach[\component]\) to denote the value of \(\mach\) at
\(\component\)  and \(\mach[v]\) as shorthand for \(\mach[|v|]\).
